Distributions in Carlson (2017)

### 2023-01-13 notebooks/Distributions_Carlson_2017.qmd
Updates use of pipe to comply with style guide and make the response simulation easier to understand

```{r simulate-responses}
sim_responses <- sim_traits |>
  full_join(
    item_parameters          |>
      unnest(`Level admin.`) |>
      select(Item, `Level admin.`, d:a_2),
    by = c(level = "Level admin.")
  )        |>
  mutate(
    prob     = (1 + exp(- (V1 * a_1 + V2 * a_2 + d)))^(-1),
    response = prob |> rbinom(n = n(), size = 1)
  )
```

>>>>

```{r simulate-responses}
item_params_by_level <- item_parameters |>
      unnest(`Level admin.`)            |>
      select(Item, level = `Level admin.`, d:a_2)

sim_responses <- sim_traits                     |>
  full_join(item_params_by_level, by = "level") |>
  mutate(
    prob     = (1 + exp(- (V1 * a_1 + V2 * a_2 + d)))^(-1),
    response = prob |> rbinom(n = n(), size = 1)
  )
```
